Optimal Algorithms for Dynamic Balanced Graph Partitioning

### 2020-05-14 paper/disc20clustering.tex
cleanup
figure 1

\begin{figure}[H]
	\centering
	\includegraphics[width=0.3\textwidth]{figs/substitute}
	\caption{todo.}
	\label{fig:lb}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.3\textwidth]{figs/substitute}
	\caption{an unsaturated edge that is inside a~component. If there is a~space next to it, maybe cluster types should fit next to it? Not sure.}
\end{figure}

@@

\noindent
\textbf{Algorithm ReMatch.} 
The algorithm ReMatch (\RM) maintains a~counter $C_{\set{x,y}}$ for each pair of nodes $\set{x,y}$ and increments it on every remote request between $x$ and $y$.
Once $C_{\set{x,y}} = \lambda$,
it resets the counter $C_{\set{x,y}}:=0$ and collocates the pair by swapping $x$ with the node collocated with $y$.

@@

\noindent
\textbf{The charging scheme.}
We charge both \OPT and \RM whenever \RM collocates a~pair.%(i.e., on a~collocation event).
\RM collocates a~pair always with a~swap,%(i.e., two simultaneous migrations),
which  costs $2\alpha$,
while \OPT may save some costs by collocating multiple pairs at once.
% before they inflict too much communication cost.
 Therefore it pays the price of only one migration per pair  (\mahmoud{see Figure \ref{fig:TBD}}).
Hence,
whenever \OPT collocates a~pair,
we charge it only the cost of moving a~single node to the cluster of the other,
i.e., $\alpha$ (in contrast to $2\alpha$ on \RM).

@@

	Next, we sum up all costs incurred by \OPT.
	By definitions of $R_t$ and $R^*_{\{u,v\}}$, we have either
	$R_{t'} \cap R_t = \sigma_{\{u,w\}}$ or
	$R_{t'} \cap R^*_{\{u,v\}} = \sigma_{\{u,w\}}$
	(\mahmoud{See figure \ref{fig:doubleCount}}). 
	This means,
	$\OPT ( \sigma_{\{u,w\}})$
	is counted at most twice in each of  the expressions
	$\OPT (R_{t'}) + \OPT (R_t)$
	and  
	$\OPT (R_{t'}) + \OPT(R^*_{\{u,v\}})$.
	Hence,
	for all collocations performed by \RM,
	and for final requests at $t=m$,
	\OPT pays at least 
	$\frac{1}{2}(
	\sum_{ t \in T } \OPT (R_t) +
	\sum_{\{u,v\}}\OPT (R^*_{\{u,v\}})
	) $.
	Then,
	the total cost to \OPT is
	\begin{align*} 	%\label{eq:costOPT}
		\OPT (\sigma)
		&=
		\frac{1}{2}
		\Big(
		\sum_{ t \in T} \OPT (R_t) 
		+ \sum_{\{u,v\}}\OPT (R^*_{\{u,v\}})
		\Big)	
		\geq
%		\Big(
%		\sum_{ t \in T} \min{ \{ \lambda, \alpha \}}  +
%		\sum_{\{u,v\}} \min{ \{C^{m}_{\{u,v\}} , \alpha \} } 
%		\Big)		
%		=
		\frac{1}{2}		
		\Big(
		\sum_{ t \in T} \alpha  
		+ \sum_{\{u,v\}} C^{m}_{\{u,v\}}
		\Big),
	\end{align*}
and
$
	\RM(\sigma)	/
	\OPT (\sigma)
	\leq
	2\Big(
	\sum_{ t \in T} 3\alpha +
	\sum_{\{u,v\}} C^{m}_{\{u,v\}}
	\Big)	 \big /
	\Big(
	\sum_{ t \in T} \alpha  
	+ \sum_{\{u,v\}} C^{m}_{\{u,v\}}  
	\Big) 	\leq 6.
$
\end{proof}

@@

\maciek{Make it more general (essentially the pseudocode of DET) to also link to this section from k=3.}

\maciek{todo: intro to the algorithm (mostly about the choice of repartition procedure in \TAlg and PPL)}

>>>>

@@

%\begin{figure}[H]
%	\centering
%	\includegraphics[width=0.3\textwidth]{figs/substitute}
%	\caption{an unsaturated edge that is inside a~component. If there is a~space next to it, maybe cluster types should fit next to it? Not sure.}
%\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.4\textwidth]{figs/cyclic}
	\caption{
		\OPT  collocates 5 pairs, paying one migration per pair.
	Dashed lines represent requests.
	An arrow, e.g.~from $b_1$ to $a_1$ means  that $b_1$ replaces $a_1$. }
	\label{fig:cyclic}
\end{figure}

%\medskip
\noindent
\textbf{Algorithm ReMatch.} 
The algorithm ReMatch (\RM) maintains a~counter $C_{\set{x,y}}$ for each pair of nodes $\set{x,y}$ and increments it on every remote request between $x$ and $y$.
Once $C_{\set{x,y}} = \lambda$,
it resets the counter $C_{\set{x,y}}:=0$ and collocates the pair by swapping $x$ with the node collocated with $y$.

@@

\noindent
\textbf{The charging scheme.}
We charge both \OPT and \RM whenever \RM collocates a~pair.%(i.e., on a~collocation event).
\RM collocates a~pair always with a~swap,%(i.e., two simultaneous migrations),
which  costs $2\alpha$,
while \OPT may save some costs by collocating multiple pairs at once.
% before they inflict too much communication cost.
 Therefore it pays the price of only one migration per pair  (see Figure \ref{fig:cyclic}).
Hence,
whenever \OPT collocates a~pair,
we charge it only the cost of moving a~single node to the cluster of the other,
i.e., $\alpha$ (in contrast to $2\alpha$ on \RM).

@@

	Next, we sum up all costs incurred by \OPT.
	By definitions of $R_t$ and $R^*_{\{u,v\}}$, we have either
	$R_{t'} \cap R_t = \sigma_{\{u,w\}}$ or
	$R_{t'} \cap R^*_{\{u,v\}} = \sigma_{\{u,w\}}$.
%	(\mahmoud{See figure \ref{fig:doubleCount}}). 
	This means,
	$\OPT ( \sigma_{\{u,w\}})$
	is counted at most twice in each of  the expressions
	$\OPT (R_{t'}) + \OPT (R_t)$
	and  
	$\OPT (R_{t'}) + \OPT(R^*_{\{u,v\}})$.
	Hence,
	for all collocations performed by \RM,
	and for final requests at $t=m$,
	\OPT pays at least 
	$\frac{1}{2}(
	\sum_{ t \in T } \OPT (R_t) +
	\sum_{\{u,v\}}\OPT (R^*_{\{u,v\}})
	) $.
	Then,
	the total cost to \OPT is
	\begin{align*} 	%\label{eq:costOPT}
		\OPT (\sigma)
		&=
		\frac{1}{2}
		\Big(
		\sum_{ t \in T} \OPT (R_t) 
		+ \sum_{\{u,v\}}\OPT (R^*_{\{u,v\}})
		\Big)	
		\geq
%		\Big(
%		\sum_{ t \in T} \min{ \{ \lambda, \alpha \}}  +
%		\sum_{\{u,v\}} \min{ \{C^{m}_{\{u,v\}} , \alpha \} } 
%		\Big)		
%		=
		\frac{1}{2}		
		\Big(
		\sum_{ t \in T} \alpha  
		+ \sum_{\{u,v\}} C^{m}_{\{u,v\}}
		\Big),
	\end{align*}
and
$
	\RM(\sigma)	/
	\OPT (\sigma)
	\leq
	2\Big(
	\sum_{ t \in T} 3\alpha +
	\sum_{\{u,v\}} C^{m}_{\{u,v\}}
	\Big)	 \big /
	\Big(
	\sum_{ t \in T} \alpha  
	+ \sum_{\{u,v\}} C^{m}_{\{u,v\}}  
	\Big) 	\leq 6.
$
\end{proof}

@@
